Figure Extra

### 2023-12-15 Figures/Figures_nonTCGA.Rmd
Fix problem Macrophage naming. Stupid bug

```{r}
benchmark_corrplots <- function(deconv_data, true_estimates, dict, key, title){
  # build the data to parse all the estimations to ground truth
  true_subset_ <- true_estimates %>%  na.exclude() %>%
    arrange(factor(get(key), levels = get(key))) %>%
    dplyr:::rename_with(~str_replace(.,"_", ".")) %>%
    dplyr:::rename_with(~str_replace(.," ", "."))

@@

  # Correlate predictions to ground truth
  to_corr <- inner_join(true_subset, deconv_subset_summary) %>% dplyr::select(-any_of(key))
  ct_corrplots <- list()
  store_corrs <- tibble(measure1 = character(),
                          measure2 = character(),
                          r = numeric(),
                          n = numeric(),
                          p = numeric(),
                          sig_p = logical(),
                          p_if_sig = numeric(),
                          r_if_sig = numeric())

@@

dict_Nakamura2018[["Quantiseq"]] <- list(CD4 = c("T.cell.CD4+.(non-regulatory)"), # "T.cell.regulatory(Tregs)"
                                   CD8 = c("T.cell.CD8+"),
                                   NK = c("NK.cell"))

@@

```{r}
# Lists of celltypes of each signature
## signature dictionary construction (can use . as regexp!)
## uncoment print of functions to check that you detect what you want.
## non matching signatures/methods (all 0) are removed.
dict_Vanderbilt <- list()
dict_Vanderbilt[["BPRNACan"]] <- list(`B cells` = c("B"),
                                      CD4 = c("CD4"),
                                      CD8 = c("CD8"),
                                      `Endothelial cells` = c(),
                                      Cancer = c("cancer"),
                                      Fibroblasts = c(),
                                      `M1 Macrophages` = c("M1"),
                                      `M2 macrophages` = c("M2"),
                                      `Mast cells` = c(),
                                      `Mural cells` = c(),
                                      NK = c("NK"),
                                      `Plasma B cells` = c(),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c(),
                                      `T reg. cells` = c()) # Missing Monocytes, M0 and Neutrophils

@@

dict_Vanderbilt[["CBSX_Fig2ab-NSCLC_PBMCs_scRNAseq_sigmatrix"]] <- list(`B cells` = c("B_cells"),
                                      CD4 = c("T.cells.CD4"),
                                      CD8 = c("T.cells.CD8"),
                                      `Endothelial cells` = c(),
                                      Cancer = c(),
                                      Fibroblasts = c(),
                                      `M1 Macrophages` = c(),
                                      `M2 macrophages` = c(),
                                      `Mast cells` = c(),
                                      `Mural cells` = c(),
                                      NK = c("NK"), # NKT.cells?
                                      `Plasma B cells` = c(),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c(),
                                      `T reg. cells` = c()) # Missing Monocytes and NKT.cells

dict_Vanderbilt[["CBSX_LM22"]] <- list(`B cells` = c("B.cells.memory", "B.cells.naive"),
                                      CD4 = c("T.cells.CD4.memory.activated", "T.cells.CD4.memory.resting", "T.cells.CD4.naive"),
                                      CD8 = c("T.cells.CD8", "T.cells.gamma.delta"),
                                      `Endothelial cells` = c(),
                                      Cancer = c(),
                                      Fibroblasts = c(),
                                      `M1 Macrophages` = c("Macrophages.M1"),
                                      `M2 macrophages` = c("Macrophages.M2"),
                                      `Mast cells` = c("Mast.cells.activated", "Mast.cells.resting"),
                                      `Mural cells` = c(),
                                      NK = c("NK.cells.activated", "NK.cells.resting"), 
                                      `Plasma B cells` = c("Plasma.cells"),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c("T.cells.follicular.helper"),
                                      `T reg. cells` = c("T.cells.regulatory..Tregs.")) # Missing Dendritic.cells.activated, Dendritic.cells.resting, Eosinophils, Macrophages.M0, , Monocytes, Neutrophils

dict_Vanderbilt[["CBSX_scRNA-Seq_melanoma_Tirosh_sigmatrix_SuppFig_3-b"]] <- list(`B cells` = c("B.cells"),
                                      CD4 = c("T.cells.CD4"),
                                      CD8 = c("T.cells.CD8"),
                                      `Endothelial cells` = c("Endothelial.cells"),
                                      Cancer = c("Malignant"),
                                      Fibroblasts = c("CAF"),
                                      `M1 Macrophages` = c(),
                                      `M2 macrophages` = c(),
                                      `Mast cells` = c(),
                                      `Mural cells` = c(),
                                      NK = c("NK.cells"), 
                                      `Plasma B cells` = c(),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c(),
                                      `T reg. cells` = c()) # Missing Macrophages

list(`B cells` = c(),
                                      CD4 = c(),
                                      CD8 = c(),
                                      `Endothelial cells` = c(),
                                      Cancer = c(),
                                      Fibroblasts = c(),
                                      `M1 Macrophages` = c(),
                                      `M2 macrophages` = c(),
                                      `Mast cells` = c(),
                                      `Mural cells` = c(),
                                      NK = c(), 
                                      `Plasma B cells` = c(),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c(),
                                      `T reg. cells` = c())

dict_Vanderbilt[["CBSX_sigmatrix_HNSCC_Fig2cd"]] <- list(`B cells` = c("B.cells"),
                                      CD4 = c("T.cells.CD4"),
                                      CD8 = c("T.cells.CD8"),
                                      `Endothelial cells` = c(),
                                      Cancer = c("Malignant.cells"),
                                      Fibroblasts = c("CAFs"),
                                      `M1 Macrophages` = c(),
                                      `M2 macrophages` = c(),
                                      `Mast cells` = c("Mast.cells"),
                                      `Mural cells` = c(),
                                      NK = c(), 
                                      `Plasma B cells` = c(),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c(),
                                      `T reg. cells` = c()) # Missing Dendritic.cells Macrophages

dict_Vanderbilt[["Quantiseq"]] <- list(`B cells` = c("B_cell"),
                                      CD4 = c("T_cell_CD4+_(non-regulatory)"),
                                      CD8 = c("T_cell_CD8+"),
                                      `Endothelial cells` = c(),
                                      Cancer = c(),
                                      Fibroblasts = c(),
                                      `M1 Macrophages` = c("Macrophage_M1"),
                                      `M2 macrophages` = c("Macrophage_M2"),
                                      `Mast cells` = c(),
                                      `Mural cells` = c(),
                                      NK = c("NK_cell"), 
                                      `Plasma B cells` = c(),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c(),
                                      `T reg. cells` = c("T_cell_regulatory_(Tregs)")) # Missing Monocyte Myeloid_dendritic_cell Neutrophil uncharacterized_cell

dict_Vanderbilt[["Quantiseq"]] <- list(CD4 = c("T.cell.CD4+.(non-regulatory)"), # "T.cell.regulatory(Tregs)"
                                   CD8 = c("T.cell.CD8+"),
                                   NK = c("NK.cell"))

>>>>

```{r}
benchmark_corrplots <- function(deconv_data, true_estimates, dict, key, title){
  # build the data to parse all the estimations to ground truth
  true_subset_ <- true_estimates %>%  na.exclude() %>%
    arrange(factor(get(key), levels = get(key))) %>%
    dplyr:::rename_with(~str_replace_all(.,"_", ".")) %>%
    dplyr:::rename_with(~str_replace_all(.," ", "."))

@@

  # Correlate predictions to ground truth
  to_corr <- inner_join(true_subset, deconv_subset_summary) %>% dplyr::select(-any_of(key))
  ct_corrplots <- list()

  ## Build matrix to store correlations 
  store_corrs <- tibble(measure1 = character(),
                          measure2 = character(),
                          r = numeric(),
                          n = numeric(),
                          p = numeric(),
                          sig_p = logical(),
                          p_if_sig = numeric(),
                          r_if_sig = numeric())

@@

dict_Nakamura2018[["Quantiseq"]] <- list(CD4 = c("T.cell.CD4+.(non-regulatory)"), # "T.cell.regulatory(Tregs)"
                                   CD8 = c("T.cell.CD8+"),
                                   NK = c("NK.cell"))
```
## Corrplot

@@

```{r}
# Lists of celltypes of each signature
## signature dictionary construction (can use . as regexp!)
## uncoment print of functions to check that you detect what you want.
## non matching signatures/methods (all 0) are removed.
dict_Vanderbilt <- list()
dict_Vanderbilt[["BPRNACan"]] <- list(`B cells` = c("B"),
                                      CD4 = c("CD4"),
                                      CD8 = c("CD8"),
                                      `Endothelial cells` = c(),
                                      Cancer = c("cancer"),
                                      Fibroblasts = c(),
                                      `M1 macrophages` = c("M1"),
                                      `M2 macrophages` = c("M2"),
                                      `Mast cells` = c(),
                                      `Mural cells` = c(),
                                      NK = c("NK"),
                                      `Plasma B cells` = c(),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c(),
                                      `T reg. cells` = c()) # Missing Monocytes, M0 and Neutrophils

@@

dict_Vanderbilt[["CBSX_Fig2ab-NSCLC_PBMCs_scRNAseq_sigmatrix"]] <- list(`B cells` = c("B_cells"),
                                      CD4 = c("T.cells.CD4"),
                                      CD8 = c("T.cells.CD8"),
                                      `Endothelial cells` = c(),
                                      Cancer = c(),
                                      Fibroblasts = c(),
                                      `M1 macrophages` = c(),
                                      `M2 macrophages` = c(),
                                      `Mast cells` = c(),
                                      `Mural cells` = c(),
                                      NK = c("NK"), # NKT.cells?
                                      `Plasma B cells` = c(),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c(),
                                      `T reg. cells` = c()) # Missing Monocytes and NKT.cells

dict_Vanderbilt[["CBSX_LM22"]] <- list(`B cells` = c("B.cells.memory", "B.cells.naive"),
                                      CD4 = c("T.cells.CD4.memory.activated", "T.cells.CD4.memory.resting", "T.cells.CD4.naive"),
                                      CD8 = c("T.cells.CD8", "T.cells.gamma.delta"),
                                      `Endothelial cells` = c(),
                                      Cancer = c(),
                                      Fibroblasts = c(),
                                      `M1 macrophages` = c("Macrophages.M1"),
                                      `M2 macrophages` = c("Macrophages.M2"),
                                      `Mast cells` = c("Mast.cells.activated", "Mast.cells.resting"),
                                      `Mural cells` = c(),
                                      NK = c("NK.cells.activated", "NK.cells.resting"), 
                                      `Plasma B cells` = c("Plasma.cells"),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c("T.cells.follicular.helper"),
                                      `T reg. cells` = c("T.cells.regulatory..Tregs.")) # Missing Dendritic.cells.activated, Dendritic.cells.resting, Eosinophils, Macrophages.M0, , Monocytes, Neutrophils

dict_Vanderbilt[["CBSX_scRNA-Seq_melanoma_Tirosh_sigmatrix_SuppFig_3-b"]] <- list(`B cells` = c("B.cells"),
                                      CD4 = c("T.cells.CD4"),
                                      CD8 = c("T.cells.CD8"),
                                      `Endothelial cells` = c("Endothelial.cells"),
                                      Cancer = c("Malignant"),
                                      Fibroblasts = c("CAF"),
                                      `M1 macrophages` = c(),
                                      `M2 macrophages` = c(),
                                      `Mast cells` = c(),
                                      `Mural cells` = c(),
                                      NK = c("NK.cells"), 
                                      `Plasma B cells` = c(),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c(),
                                      `T reg. cells` = c()) # Missing Macrophages

dict_Vanderbilt[["CBSX_sigmatrix_HNSCC_Fig2cd"]] <- list(`B cells` = c("B.cells"),
                                      CD4 = c("T.cells.CD4"),
                                      CD8 = c("T.cells.CD8"),
                                      `Endothelial cells` = c(),
                                      Cancer = c("Malignant.cells"),
                                      Fibroblasts = c("CAFs"),
                                      `M1 macrophages` = c(),
                                      `M2 macrophages` = c(),
                                      `Mast cells` = c("Mast.cells"),
                                      `Mural cells` = c(),
                                      NK = c(), 
                                      `Plasma B cells` = c(),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c(),
                                      `T reg. cells` = c()) # Missing Dendritic.cells Macrophages

dict_Vanderbilt[["Quantiseq"]] <- list(`B cells` = c("B_cell"),
                                      CD4 = c("T_cell_CD4+_(non-regulatory)"),
                                      CD8 = c("T_cell_CD8+"),
                                      `Endothelial cells` = c(),
                                      Cancer = c(),
                                      Fibroblasts = c(),
                                      `M1 macrophages` = c("Macrophage_M1"),
                                      `M2 macrophages` = c("Macrophage_M2"),
                                      `Mast cells` = c(),
                                      `Mural cells` = c(),
                                      NK = c("NK_cell"), 
                                      `Plasma B cells` = c(),
                                      `T cells proliferative` = c(),
                                      `T helper cells` = c(),
                                      `T reg. cells` = c("T_cell_regulatory_(Tregs)")) # Missing Monocyte Myeloid_dendritic_cell Neutrophil uncharacterized_cell
